Initial Analysis

### 2020-08-03 Scripts/Initial_Analysis.Rmd
updated finction of fig 1

@@

@@

Entity_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_Results_Trans,
            by = "eez_name") %>% 
  group_by(fishing_entity) %>% 
  summarise(Size_Entity = sum(Area_km2))

@@

@@

```{r comparriosn_wtih_teh}

@@

Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).

@@

Discrete <- Clean_Results_Trans %>% 
  filter(
    area_index < Min_AI |
    area_index > Max_AI |
    model_index < MI
  ) %>% 
  group_by(taxon_key,fishing_entity,eez_name) %>% 
  summarise(n()) %>% 
  anti_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity")) %>% 
  left_join(Clean_sau_eez_fes)

# Both categories (trans and Discrete)
n_discrete <- Tresholded_T_Data %>% 
  semi_join(Discrete,
            by = "taxon_key") %>% # those that are not only discrete
  group_by(taxon_key) %>% 
  summarise(n()) %>% 
  pull(unique(taxon_key)) %>% 
  length()

Summary_Discrete <- SAU_Sampled_Data %>% 
  semi_join(Discrete,
            by = c("taxon_key","fishing_entity_id")
  ) %>% 
  group_by(Variable) %>%
  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
         Per_SAU = Total_Trans/Total_Global*100)

@@

## double check

@@

# Total species
n_discrete_exclusive + n_trans # 938

@@

EEZ_Area <- World_sf %>% 
  as.data.frame() %>% 
  group_by(eez_id) %>% 
  summarise(Size_EEZ = sum(Area_km2))

Entity_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_Results_Trans,
            by = "eez_name") %>% 
  group_by(fishing_entity) %>% 
  summarise(Size_Entity = sum(Area_km2))

# Data per Territory (EEZ)
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_id) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  left_join(EEZ_Area,
            by = "eez_id") %>%
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
    Weight_Bins = cut(Weight_Spp,breaks = 5),
    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                           labels = c('super low', 'low','median', 'high','super high')
    )
  )

@@

# Set manual breaks for bins
Map_Breaks <- c(-1,10,100,1000,2000,12000) 
# Map_Breaks <- c(-1,20,200,2000,1000,20000)

###

Total_Value_EEZ <- Clean_sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(SAU_Global_Data) %>% 
  group_by(fishing_entity,Variable) %>% 
  summarise(Total_Value = sum(Value,na.rm=T))

Value_Trans_Country <- Clean_sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(Tresholded_T_Data,
            by = c("fishing_entity","fishing_entity_id")
            ) %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
                         )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  left_join(Entity_Area,
            by = "fishing_entity") %>%
  # Include the weighted method for supplementals
  mutate_at(
    vars(catch,value),
    funs(weight= ./(Size_Entity/1000000))
  ) %>%
  gather("Variable","Value",catch:value,catch_weight:value_weight) %>%
  # gather("Variable","Value",catch:value) %>%
  group_by(fishing_entity,Variable,Value) %>% 
  mutate(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_EEZ,
            by = c("fishing_entity", "Variable") 
            ) %>% # uncomment for estimating percentage
  # Convert catch to million tonnes
  ungroup() %>% 
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                         Value),
    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
  )

### Data for continental analysis

@@

## Sub region leven

Subregion_Trans_raw_Value <- Value_Trans_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region,Variable) %>% 
  summarise_if(is.numeric,c(sum = sum,
                            m = mean,
                            sd = sd),
               na.rm=T) %>%
  arrange(Variable) %>%
  ungroup() %>% 
  mutate(id = rep(seq(1,17),2)) %>% 
  mutate(Value_sum=ifelse(Variable == "catch" & Value_sum >= 12,12,Value_sum))

@@

Transboundary_Spp %>% anti_join(World_sf, by = "eez_id")

@@

# Label info Rev
label_data_rev <- Subregion_Trans_Value %>% 
  filter(Variable == "value") %>% 
  arrange(Value_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,number_of_bar),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )#,
    # sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
  )

# Label info Catch
label_data_catch <- Subregion_Trans_Value %>% 
  filter(Variable == "catch") %>% 
  arrange(Value_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,number_of_bar),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )#,
    # sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
  )

@@

# Variable to plot (value or catch)
Variable_plot <- "catch"
CreateFigureOne(Variable_plot)

>>>>

  if(Variable_Selected == "value"){

@@

  }else{
    ggsave(
      plot = Map,
      width = 17,
      height = 12,
      units = "in",
      filename = Plot_Name
    )
  }

@@

@@

### Duble check for NA's
# map(Tresholded_T_Data, ~sum(is.na(.))) # No NA's

@@

```{r comparison_with_Teh_2015, eval = T, echo = F}

@@

Based on our assessment (see Methods), 582 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).

@@

Discrete <- Clean_Results_Trans %>% 
  filter(
    area_index < Min_AI |
      area_index > Max_AI |
      model_index < MI
  ) %>% 
  # Needed to correct for names
  select(-fishing_entity) %>% 
  left_join(Clean_sau_eez_fes,
            by = "eez_name") %>% 
  # Remove Countries that share with other countries
  anti_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity")
  )

### Duble check for NA's
# map(Discrete, ~sum(is.na(.))) # No NA's

# Both categories (trans and Discrete)
n_discrete <- Tresholded_T_Data %>% 
   # Filter species that are also discrete
  filter(taxon_key %in% Discrete$taxon_key) %>% 
  group_by(taxon_key) %>% 
  summarise(n()) %>% 
  pull(unique(taxon_key)) %>% 
  length()

# Summary results for paper
Summary_Discrete <- SAU_Sampled_Data %>% 
  semi_join(Discrete,
            by = c("taxon_key","fishing_entity_id")
  ) %>% 
  group_by(Variable) %>%
  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
         Per_SAU = Total_Trans/Total_Global*100)

@@

## Double check no double counting

@@

# Double check n = total species (938)
n_discrete_exclusive + n_trans # 938

@@

# Get the area of each eez provided in the shapefile 
EEZ_Area <- World_sf %>% 
  as.data.frame() %>% 
  group_by(eez_id) %>% 
  summarise(Size_EEZ = sum(Area_km2)) %>% 
  left_join(Clean_sau_eez_fes)

Entity_Area <- EEZ_Area %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(Size_entity = sum(Size_EEZ)
            )

# Data per Territory (EEZ)
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_id,eez_name) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  left_join(EEZ_Area,
            by = c("eez_id","eez_name")
            ) %>%
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
    Weight_Bins = cut(Weight_Spp,breaks = 5),
    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                           labels = c('super low', 'low','median', 'high','super high')
    )
  )

@@

# Set manual breaks for bins
Map_Breaks <- c(-1,10,100,1000,5000,12000)

### Data for land polygon
# Total_Value_Entity <- Clean_sau_eez_fes %>% 
#   group_by(fishing_entity_id, fishing_entity) %>% 
#   summarise(n=n()) %>% # Get all of the fishing entity and id
#   select(-n) %>% 
#   left_join(SAU_Global_Data) %>% 
#   group_by(fishing_entity,Variable) %>% 
#   summarise(Total_Value = sum(Value,na.rm=T))

# Estimate value per fishing entity
Total_Value_Entity <- SAU_Global_Data %>% 
  group_by(fishing_entity_id,Variable) %>% 
  summarise(Total_Value = sum(Value,na.rm=T))

# Data for map

Value_Trans_Country <- Tresholded_T_Data %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity_id,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
    )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  left_join(Entity_Area,
            by = c("fishing_entity_id")
            ) %>%
  # Include the weighted method for supplementals
  mutate_at(
    vars(catch,value),
    funs(weight= ./(Size_entity/1000000))
  ) %>%
  gather("Variable","Value",catch:value,catch_weight:value_weight) %>%
  # gather("Variable","Value",catch:value) %>%
  group_by(fishing_entity,Variable,Value) %>% 
  mutate(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_Entity,
            by = c("fishing_entity_id", "Variable") 
  ) %>% # uncomment for estimating percentage
  # Convert catch to million tonnes
  ungroup() %>% 
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                   Value),
    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
  )

### Data for continental analysis (round bar plots)

@@

## Sub region leven
Subregion_Trans_raw_Value <- Value_Trans_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region,Variable) %>% 
  summarise_if(is.numeric,c(sum = sum,
                            m = mean,
                            sd = sd),
               na.rm=T) %>%
  arrange(Variable) %>%
  ungroup() %>% 
  mutate(id = rep(seq(1,17),4)) %>% 
  mutate(Value_sum=ifelse(Variable == "catch" & Value_sum >= 12,12,Value_sum))

@@

# Douuble check we are not missing EEZs
# Transboundary_Spp %>% anti_join(World_sf, by = "eez_id")

@@

# Label info Rev
label_data_rev <- Subregion_Trans_Value %>% 
  filter(Variable == "value") %>% 
  arrange(Value_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,number_of_bar),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               ifelse(sub_region =="Sub-Saharan Africa","Sub-Saharan\nAfrica",
                               paste(sub_region))
                        )
    )#,
    # sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
  )

# Label info Catch
label_data_catch <- Subregion_Trans_Value %>% 
  filter(Variable == "catch") %>% 
  arrange(Value_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,number_of_bar),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               ifelse(sub_region =="Sub-Saharan Africa","Sub-Saharan\nAfrica",
                                      paste(sub_region))
                        )
    )
  )

@@

# Variable to plot (value,  catch, weighted_catch, weighted_value)
Variable_plot <- "value"
CreateFigureOne(Variable_plot)
